The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-24 article.tex
Started writing the MDL molfile section

>>>>

The MDL molfile formats are still very popular, despite it being a proprietary
standard, but taking advantage of the detailed specification still floating
around on the world wide web and can be found by googling for
ctfile.pdf~\cite{ctfile.pdf}. The CDK has various related readers, reflecting
the various formats specified in this document, as well as a more historical
reader for the pre-V2000 formats. When this reader was written, MDL molfiles
in this pre-V2000 format were still around, but the authors are unaware of
existing use of this format. At the same time, V3000 does not have seen a
significant adoption either. Furthermore, several formats exist that wrap
molfiles in collections, such as structure data files (SD files), reaction files,
and reaction collections. Table XXX shows an overview of the various readers
for (partially) supported formats.
% note, I pie chart would be cool, showing the various relative amounts of the
% various formats.

Of course, the molfile is special here and this reader has been rewritten in
this CDK version, and now supports....
